%-------------------------
% Rover Resume - Base Template
% Link: https://github.com/subidit/rover-resume
% Shows code for various formatting options for different resume sections.
% Education and Projects have single-line headers; while Experience uses double-line.
% Some formatting codes are kept inline; consider \newcommand{cmd}{def}.
% Excludes hyperref and icons for readability; MVP version.
% Mix and match as desired. Be consistent with headers and sub-headers.
%------------------------

\documentclass[11pt]{article} % font size 10pt/11pt/12pt

\usepackage[margin=0.75in, a4paper]{geometry}
\setcounter{secnumdepth}{0} % remove section numbering
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0} % remove vertical spacing above and below
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\large\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,left=0pt .. \parindent}
\pagestyle{empty} % remove page number
\pdfgentounicode=1


\begin{document}

% === Header ======================================================================================
\begin{center}
	\begin{minipage}{0.45\textwidth}
		{\Huge\bfseries
			Mostafa Rezaee  % Name Here
		} \\ \medskip
		Ph.D. in Data Science \\ % Title [optional]
		Data Scientist $|$ ML Engineer $|$ AI Scientist 
	\end{minipage} \hfill
	\begin{minipage}{0.48\textwidth}
		%\raggedleft
		GitHub: github.com/0-mostafa-rezaee-0 \\
		LinkedIn: linkedin.com/mostafa-rezaee \\
		Email: mostafa.mohammadrezaee@gmail.com \\
		Mobile: 4193157481
	\end{minipage}
\end{center}

% === Summary =====================================================================================
\section{Summary}
%=================
\begin{itemize}
	\item Aaa
	\item Bbb
	\item My GitHub Repo Lists: LLMs, AI Engineering, ML Engineering, Recommender Systems, Causal Inference, A/B Testing, Physics \& Engineering, Personal Branding.
\end{itemize}

% === Experience ==================================================================================
\section{Experience}
\subsection{Machine Learning Engineer}
\subsubsection{Stealth Startup \hfill May 2024 - Present}
\begin{itemize}
	\item Deployed scalable ML models as REST APIs using FastAPI and Docker, integrating PostgreSQL for persistent prediction storage.
	\item Implemented real-time monitoring with Prometheus and Grafana, tracking API performance, model predictions, and system health. 
	\item Automated ML workflows with CI/CD pipelines, enabling seamless model updates, containerized deployments, and continuous integration using GitHub Actions.
\end{itemize}

\subsection{Data Scientist}
\subsubsection{SaveBirds \hfill Sep 2019 - Apr 2024}
\begin{itemize}
	\item 99\% reduction in data preparation and analysis time—cutting it from 90 days to just 1 minute—by developing the SaveBirds.app, enabling ecologists and conservationists without coding skills to access 56 years of 800 bird species from 300,000 locations across North America.
	\item 99\% reduction in atlas creation time—cutting it from 180 days to under 10 hours—by creating the Bird Atlas Generator (BAG), making it accessible without advanced GIS expertise.
	\item Automated key biodiversity metrics calculation enabling rapid, data-driven conservation decisions for 40,000 Protected Areas and supporting the \$75 billion wildlife-watching industry.
	\item Supported 7 projects involving 10 researchers from 6 institutions.
\end{itemize}

\subsection{AI Scientist}
\subsubsection{Sanofi \hfill Jun 2022 - Aug 2022}
\begin{itemize}
	\item Boosted Gait Speed Accuracy: Improved accuracy by 25\% (70\% to 88\%), reducing MAE from 0.12 m/s to 0.098 m/s. (Technology: LSTM, Accelerometer Data).
	\item Refined Step Segmentation: Increased precision in distinguishing left vs. right steps from 86\% to 94\%, reducing misclassification rates by 57\% (14\% to 6\%). (Technology: Random Forest, SVM, Signal Processing)	
	\item Minimized False Positives in Sway Detection: Improved accuracy in detecting sway by 46\% (65\% to 95\%), reducing false alarms from 22\% to 15\%. (Technology: Bayesian Filtering, Adaptive Thresholding, Time-Series Anomaly Detection) 
	\item Optimized Data Pipeline: Accelerated preprocessing of 1.2 million accelerometer data points, reducing processing time by 45\% (9.2s to 5.1s). (Technology: Apache Spark, Feature Engineering)
\end{itemize}

\subsection{Lead Data Scientist \& Deputy Director of Research and Technology}
\subsubsection{Farabi Institute \hfill Sep 2013 - Aug 2019}
\begin{itemize}
	\item Led the provincial implementation of a nationwide data digitization project, transforming the educational ecosystem for over 1,000,000 students, 40,000 classrooms, and 76,000 teachers across 40 districts.
	\item Supervised a team of 100+ data analysts directly reporting to me, ensuring standardized, high-quality data collection and analysis at scale. 
	\item Enhanced data accuracy by 40\% and established real-time updates, allowing instant visibility into changes in student, teacher, and school profiles.
	\item Applied advanced regression, classification, and time series analyses to derive actionable insights, guiding data-driven policy decisions for senior authorities.
	\item Developed an automated alert system that identified significant performance shifts, prompting timely interventions and continuous improvement throughout the education system.
\end{itemize}

\subsection{Adjunct Professor of Machine Learning and Computational Studies}
\subsubsection{Payame Noor University (PNU) \hfill Sep 2013 - Aug 2019}
\begin{itemize}
	\item Empowered 600+ students over six years by teaching a 3-credit Computer Programming course each semester, covering Python and Machine Learning to 50+ senior and master's students per class.
	\item Supervised 100+ senior students' final projects, designing specialized Machine Learning projects that laid the foundation for their master's research and careers in AI.
	\item Shaped the future of AI professionals by inspiring students to integrate Machine Learning into their master's projects, fostering a new generation of ML practitioners and researchers.
\end{itemize}

% === Education ===================================================================================
\section{Education}
%=================%
\subsection{Data Science, Ph.D. $|$ {\normalfont\itshape Bowling Green State University, Ohio } \hfill 2024} 
\begin{itemize}
	\item My Ph.D. Project: https://savebirds.app
\end{itemize}

% === Skills ======================================================================================
\section{Skills}
%===========================%
\begin{description}[itemsep=0pt]
	\item[Data Science] A/B Testing, Causal Inference, Recommender Systems
	\item[LLMs \& Generative AI] Transformers, OpenAI, Ray Data, LangChain, RAG
	\item[AI Engineering] FastAPI, Streamlit, Gradio, HuggingFace, ONNX Runtime, Triton, W\&B
	\item[ML Engineering] Docker, Kubernetes, MLflow, Kubeflow, Apache Airflow, SageMaker
	\item[Deep Learning] Computer Vision, Natural Language Processing (NLP), HuggingFace, PyTorch, TensorFlow
	\item[Machine Learning] scikit-learn, caret
	\item[Cloud Platforms] AWS, Azure, Google Cloud
	\item[Time Series Analysis] Transformers, TCN, Prophet, LSTM, Statsmodels, ARIMA, SARIMA, TSA
	\item[Big Data] Apache Spark, Hadoop, Apache Hive, Presto, Apache Flink, Dask
	\item[Programming Languages] Python, SQL, R, C++, FORTRAN
\end{description}

\end{document}

%=================%
% \subsection{Company ABC \hfill City, State (or Remote)}
% \subsubsection{Position Title \hfill  Month Year - Month Year}
% \begin{itemize}
% 	\item Beginning with your most recent position, describe your experience, skills, and resulting outcomes in bullet or paragraph form.
% 	\item Begin each line with an action verb and include details that will help the reader understand your accomplishments, skills, knowledge, abilities, or achievements.
% 	\item Quantify where possible. Do not use personal pronouns; each line should be a phrase rather than a full sentence.
% \end{itemize}

% % === Projects ====================================================================================
% \section{Projects}
% %=================
% \subsection{Project Name $|$ \normalfont\textit{github.com/project-link} \hfill 2019}
% \begin{itemize}
% 	\item Tech used, Language, Frameworks etc.
% 	\item Implemented ABC feature
% 	\item Optimized XYZ by 50\%
% \end{itemize}

% % === Certification \& Awards =====================================================================
% \section{Certification \& Awards}
% %===============================%
% \begin{enumerate}[label=\null, left=0pt..0pt, itemsep=0pt]
% 	\item Some programming bootcamp, Location. \hfill 2023
% 	\item Forbes Top 15 Procrastinators under 15. \hfill 2022
% 	\item Participation award for attending workshop. \hfill 2021
% \end{enumerate}

