\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem, hyperref, graphicx, xcolor, multicol, titlesec, parskip}
\usepackage{fancyhdr}
\usepackage{array}

% Modern sans-serif fonts
\usepackage{avant}     % For headings (similar to Montserrat)
\usepackage{helvet}    % For body text (similar to Inter)
\renewcommand{\familydefault}{\sfdefault}

% Section title formatting
\titleformat{\section}
    {\bfseries\Large}
    {}
    {0em}
    {}
    [\vspace{-0.5em}]

% Reduce spacing for sections
\titlespacing*{\section}{0pt}{6pt}{3pt}

\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1.25}

%---------------------------------------------------------------------
\begin{document}

%=========================================
% Header with two-column format
\noindent

\begin{tabular}{@{}p{3.5in} p{3.5in}@{}}

    {\bfseries\LARGE Mostafa Rezaee, Ph.D.} & \hfill LinkedIn: \href{https://www.linkedin.com/in/mostafa-rezaee/}{www.linkedin.com/in/mostafa-rezaee} \\
    
    \hline 
    
    Data Scientist | Machine Learning Engineer & \hfill Email: mostam@bgsu.edu | Phone: (419) 315-7481 \\
    Green Card Holder & \hfill Open to relocation

\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Summary}

\begin{itemize}
    \item Ph.D. in Data Science with expertise in machine learning, AI, and data analysis. Proven track record in developing scalable ML solutions, data processing pipelines, and leading large-scale data projects.
    
    \item Led the development of SaveBirds.app, processing 56 years of data on 800 bird species across 300,000 locations, reducing analysis time from weeks to minutes and enabling rapid assessment of 40,000+ Protected Areas.
    
    \item Enhanced medical wearable analytics, improving accuracy metrics by 25-57% while optimizing data processing time by 45% on 1.2M data points.
    
    \item Led nationwide data digitization project for 1M+ students across 40 districts, improving data accuracy by 40% and implementing real-time updates and alerts.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Experience}

\vspace{4pt}
%*****************************************
{\bfseries Machine Learning Engineer}, Stealth Startup, California, USA \hfill May 2024 -- Present

\begin{itemize}
    \item Deployed scalable ML models as REST APIs using FastAPI and Docker.
    
    \item Implemented real-time monitoring with Prometheus and Grafana.
    
    \item Automated ML workflows with CI/CD pipelines using GitHub Actions.
\end{itemize}

\vspace{4pt}
%*****************************************
{\bfseries Data Scientist}, SaveBirds, Ohio, USA \hfill September 2019 -- May 2024

\begin{itemize}
    \item Developed SaveBirds.app (www.savebirds.app) to reduce data processing time by 99%.
    
    \item Created the Bird Atlas Generator (BAG), making atlas creation accessible without GIS expertise.
    
    \item Automated biodiversity metrics for 40,000 Protected Areas, supporting 7 projects with 10 researchers from 6 institutions.
\end{itemize}

\vspace{4pt}
%*****************************************
{\bfseries AI Scientist}, Sanofi, Cambridge, MA, USA \hfill June 2022 -- August 2022

\begin{itemize}
    \item Improved gait speed accuracy by 25% using Long Short-Term Memory networks.
    
    \item Enhanced sway detection accuracy by 46% (65% to 95%) and reduced false alarms from 22% to 15% using Bayesian Filtering, Adaptive Thresholding, and Time-Series Anomaly Detection.
    
    \item Optimized data pipeline for 1.2 million accelerometer data points, reducing processing time by 45% using Apache Spark and advanced Feature Engineering.
\end{itemize}

\vspace{4pt}
%*****************************************
{\bfseries Lead Data Scientist \& Deputy Director of Research and Technology}, Farabi Institute \hfill September 2013 -- May 2022

\begin{itemize}
    \item Led provincial implementation of nationwide data digitization project for 1,000,000+ students, 40,000 classrooms, and 76,000 teachers across 40 districts.
   
    \item Supervised 100+ data analysts, ensuring standardized, high-quality data collection and analysis at scale.
    
    \item Enhanced data accuracy by 40% and established real-time updates for student, teacher, and school profiles.
    
    \item Applied regression, classification, and time series analyses to derive actionable insights for data-driven policy decisions.
    
    \item Developed automated alert system identifying performance shifts, enabling timely interventions throughout the education system.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}

\begin{itemize}
    \item {\bfseries Ph.D. in Data Science}, Bowling Green State University, Ohio, USA \hfill September 2019 -- May 2024
    
    \item {\bfseries M.Sc. in Physics}, University Name, Location \hfill Graduation Year
    Focus: Nonlinear Optics, thermal effects in Green Lasers
    
    \item {\bfseries B.Sc. in Physics}, University Name, Location \hfill Graduation Year
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Technical Skills}

\begin{itemize}
    \item {\bfseries Programming Languages}: Python, R, SQL, C++, FORTRAN, MATLAB
    
    \item {\bfseries Machine Learning \& AI}: TensorFlow, PyTorch, Scikit-learn, Computer Vision, NLP, LLMs, RAG
    
    \item {\bfseries Data Tools}: Pandas, NumPy, GeoPandas, ipywidgets, PostgreSQL, Prometheus, Grafana
    
    \item {\bfseries DevOps \& Infrastructure}: Docker, GitHub Actions, CI/CD, High-Performance Computing (HPC)
    
    \item {\bfseries Big Data}: Apache Hadoop, Apache Spark, Feature Engineering, Time-Series Analysis
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Publications \& Projects}

\begin{itemize}
    \item {\bfseries Publications}: 34 total publications, including 12 journal articles and 22 full conference papers
    
    \item {\bfseries Research Focus}: Generative AI in Computer Vision, Computational Modeling and Simulation
    
    \item {\bfseries SaveBirds.app}: Led 7 research projects involving 10 researchers from 6 institutions
    
    \item All computational studies employed original modeling and simulation approaches developed through self-authored code
\end{itemize}

\end{document}
%---------------------------------------------------------------------
