\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem, hyperref, graphicx, xcolor, multicol, titlesec, parskip}
\usepackage{fancyhdr}
\usepackage{array}

% Modern sans-serif fonts
\usepackage{avant}     % For headings (similar to Montserrat)
\usepackage{helvet}    % For body text (similar to Inter)
\renewcommand{\familydefault}{\sfdefault}

% Section title formatting
\titleformat{\section}
    {\bfseries\Large}
    {}
    {0em}
    {}
    [\vspace{-0.5em}]

% Reduce spacing for sections
\titlespacing*{\section}{0pt}{6pt}{3pt}

\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1.25}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
}

%---------------------------------------------------------------------
\begin{document}

%=========================================
% Header with two-column format
\noindent

\begin{tabular}{@{}p{3.5in} p{3.5in}@{}}

    {\bfseries\LARGE Jane Smith} & \hfill LinkedIn: \href{https://www.linkedin.com/in/jane-smith/}{linkedin.com/in/jane-smith} \\
    
    \hline 
    
    Software Engineer | Full Stack Developer & \hfill jane.smith@example.com | (123) 456-7890
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Summary}

\begin{itemize}
    \item Results-oriented Software Engineer with 5+ years of experience specializing in full-stack development, cloud architecture, and DevOps. Proven track record of delivering high-performance web applications resulting in 40\% improvement in user engagement.
    
    \item Successfully led the migration of legacy systems to modern microservices architecture that reduced deployment time by 75\%, leading to faster time-to-market for new features.
    
    \item Recognized for problem-solving abilities and expertise in optimizing application performance, consistently delivering 99.9\% uptime across enterprise-scale applications.
    
    \item Adept at mentoring junior developers and implementing CI/CD practices, enabling 3x faster development cycles and improved code quality.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Experience}

\vspace{4pt}
%*****************************************
{\bfseries Senior Software Engineer}, Tech Innovations Inc., San Francisco, CA \hfill January 2022 -- Present

\begin{itemize}
    \item Led cross-functional team of 8 developers to redesign the company's flagship product, resulting in 35\% increase in monthly active users and 28\% reduction in bounce rate.
    
    \item Implemented containerization strategy using Docker and Kubernetes to scale applications dynamically, improving system reliability by 45\% and reducing cloud infrastructure costs by $120K annually.
    
    \item Collaborated with product and design teams to develop and launch 5 new features, enhancing customer satisfaction scores from 7.2 to 8.9 on a 10-point scale.
    
    \item Managed the implementation of comprehensive test automation framework, increasing code coverage from 65\% to 92\% while reducing regression testing time by 70\%.
\end{itemize}

\vspace{4pt}
%*****************************************
{\bfseries Software Engineer}, DataFlow Systems, Boston, MA \hfill March 2019 -- December 2021

\begin{itemize}
    \item Spearheaded migration from monolithic architecture to microservices, resulting in 60\% improved application performance and 40\% reduction in deployment failures.
    
    \item Developed and implemented real-time data processing pipeline handling 500+ transactions per second, reducing data lag from minutes to milliseconds.
    
    \item Recognized for excellence in code quality, receiving the quarterly "Code Craftsperson" award twice in 2021.
    
    \item Trained and mentored 6 junior developers on best practices in software development, improving team velocity by 32\% over three quarters.
\end{itemize}

\vspace{4pt}
%*****************************************
{\bfseries Junior Developer}, StartUp Ventures, New York, NY \hfill June 2017 -- February 2019

\begin{itemize}
    \item Successfully delivered front-end components for the company's SaaS platform, exceeding sprint targets by 20\% consistently.
    
    \item Identified and resolved critical security vulnerabilities, leading to successful SOC 2 certification and securing three enterprise clients worth $1.2M in annual revenue.
    
    \item Streamlined build process, reducing average build time from 15 minutes to 4 minutes while maintaining comprehensive test coverage.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}

\begin{itemize}
    \item {\bfseries Master of Science in Computer Science}, Massachusetts Institute of Technology, Cambridge, MA \hfill 2017
    
    \item {\bfseries Bachelor of Science in Software Engineering}, University of California, Berkeley, CA \hfill 2015
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Technical Skills}

\begin{itemize}
    \item {\bfseries Programming Languages}: JavaScript (ES6+), TypeScript, Python, Java, Go, SQL
    
    \item {\bfseries Front-End Technologies}: React, Angular, Vue.js, Redux, HTML5, CSS3, SASS, Webpack
    
    \item {\bfseries Back-End \& Infrastructure}: Node.js, Express, Django, Spring Boot, Docker, Kubernetes, AWS, Azure, GCP
    
    \item {\bfseries Database \& Data}: PostgreSQL, MongoDB, Redis, Elasticsearch, GraphQL, REST APIs, Kafka
    
    \item {\bfseries DevOps \& Tools}: Git, GitHub Actions, Jenkins, CircleCI, Terraform, Prometheus, Grafana, ELK Stack
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Certifications}

\begin{itemize}
    \item {\bfseries AWS Certified Solutions Architect - Professional}, Amazon Web Services \hfill 2022
    
    \item {\bfseries Google Cloud Professional Cloud Architect}, Google Cloud \hfill 2021
    
    \item {\bfseries Certified Kubernetes Administrator (CKA)}, Cloud Native Computing Foundation \hfill 2020
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Projects}

\begin{itemize}
    \item {\bfseries Scalable E-commerce Platform}: Developed microservices-based e-commerce solution handling 10,000+ concurrent users with 99.99\% uptime, using React, Node.js, MongoDB, and AWS
    
    \item {\bfseries Open-Source Contribution - Data Visualization Library}: Core contributor to data visualization library with 15K+ GitHub stars; implemented 3 major features enhancing performance by 35\%
\end{itemize}

\end{document}
%--------------------------------------------------------------------- 