\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem, hyperref, graphicx, xcolor, multicol, titlesec, parskip}
\usepackage{fancyhdr}
\usepackage{array}

% Reduce spacing for sections
\titlespacing*{\section}{0pt}{6pt}{3pt}

\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1}

%---------------------------------------------------------------------
\begin{document}

%=========================================
% Header with two-column format
\noindent

\begin{tabular}{@{}p{3.5in} p{3.5in}@{}}

    \textbf{\LARGE Mostafa Rezaee, Ph.D.} & \hfill \href{https://www.linkedin.com/in/mostafa-rezaee/}{LinkedIn} \textbar{} Data Scientist \textbar{} ML Engineer \\
    
    \hline 
    
    \textbf{Ph.D. in Data Science} \textbar{} M.Sc. \& B.Sc. in Physics & \hfill \texttt{mostam@bgsu.edu} \textbar{} (419) 315-7481 \textbar{} Open to relocation.

\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Summary}

\begin{itemize}

    \item Green Card Holder
    
    \item Ph.D. in Data Science
    
    \item \textbf{ML Engineer} \\     
    Deployed and monitored scalable ML models as REST APIs using FastAPI, Docker, PostgreSQL, Prometheus, and Grafana, with automated CI/CD via GitHub Actions.
    
    \item \textbf{Data Scientist} \\ 
    Developed \href{http://savebirds.app/}{www.SaveBirds.app}, a first-of-its-kind data science web app processing 56 years of data on 800 bird species across 300,000, fueling the \href{https://www.usgs.gov/centers/eesc/science/north-american-breeding-bird-survey#:%7E:text=common%20and%20helping-,fuel%20a%20%2475%20billion%20wildlife%20watching%20industry,-.%C2%A0%C2%A0Each%20year%20thousands:~:text=helping%20fuel%20a%20%2475%20billion%20wildlife%20watching%20industry}{\$75 billion} wildlife-watching industry, reducing analysis time from weeks to minutes, enabling rapid assessment of 40,000+ Protected Areas, and supporting 7 projects with 10 researchers from 6 institutions.  
    
    \item \textbf{AI Scientist} \\
    Enhanced wearable medical device analytics, improving gait speed accuracy by 25\%, step segmentation precision by 57\%, step length estimation by 29\%, and sway detection accuracy by 46\%, while optimizing data processing time by 45\% on 1.2M data points. 
    
    \item \textbf{Lead Data Scientist} \\
    Led the provincial implementation of a nationwide data digitization project for 1,000,000+ students, 40,000 classrooms, and 76,000 teachers across 40 districts, supervising 100+ analysts, improving data accuracy by 40\%, enabling real-time updates, and deploying automated alerts for data-driven policy decisions.

    \item \textbf{Publications \& projects } \\
    - Publications (34), including 12 Journal articles \& 22 full conference papers. \\    
    - Generative AI in Computer Vision \\    
    - Projects (7) outlined in the SaveBirds.app involving 10 researchers from 6 institutions. \\     
    - All publications and projects are computational studies employing modeling and simulation approaches developed entirely through my own original code, rather than relying on existing software.     
 

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Experience}

\vspace{6pt}
%*****************************************
\hspace{3mm} \textbf{Machine Learning Engineer, Stealth Startup, California, USA} \hfill \textit{May 2024 -- Present}

\begin{itemize}

    \item Deployed scalable ML models as REST APIs using FastAPI and Docker.
    
    \item Implemented real-time monitoring with Prometheus and Grafana.
    
    \item Automated ML workflows with CI/CD pipelines.

\end{itemize}

\vspace{6pt}
%*****************************************
\hspace{3mm} \textbf{Data Scientist, SaveBirds, Ohio, USA} \hfill \textit{Sep. 2019 -- May 2024}

\begin{itemize}

    \item Developed \href{http://www.savebirds.app}{SaveBirds.app} to reduce data processing time by 99\%.
    
    \item Created the Bird Atlas Generator (BAG), making atlas creation accessible without GIS expertise.
    
    \item Automated biodiversity metrics for 40,000 Protected Areas.

\end{itemize}

\vspace{6pt}
%*****************************************
\hspace{3mm} \textbf{AI Scientist, Sanofi, Cambridge, MA, USA} \hfill \textit{Jun. 2022 -- Aug. 2022}

\begin{itemize}

    \item Improved gait speed accuracy by 25\% using LSTMs.
    
    \item Minimized False Positives in Sway Detection: Improved accuracy in detecting sway by 46\% (65\% to 95\%), reducing false alarms from 22\% to 15\%. (Technology: Bayesian Filtering, Adaptive Thresholding, Time-Series Anomaly Detection)
    
    \item Optimized Data Pipeline: Accelerated preprocessing of 1.2 million accelerometer data points, reducing processing time by 45\% (9.2s to 5.1s). (Technology: Apache Spark, Feature Engineering)

\end{itemize}

\vspace{6pt}
%*****************************************
\hspace{3mm} \textbf{Lead Data Scientist \& Deputy Director of Research and Technology}, Farabi Inst. \hfill \textit{Sep. 2013 -- May 2022}

\begin{itemize}
    
    \item Led the provincial implementation of a nationwide data digitization project, transforming the educational ecosystem for over 1,000,000 students, 40,000 classrooms, and 76,000 teachers across 40 districts.
   
    \item Supervised a team of 100+ data analysts directly reporting to me, ensuring standardized, high-quality data collection and analysis at scale.
    
    \item Enhanced data accuracy by 40\% and established real-time updates, allowing instant visibility into changes in student, teacher, and school profiles.
    
    \item Applied advanced regression, classification, and time series analyses to derive actionable insights, guiding data-driven policy decisions for senior authorities
    
    \item Developed an automated alert system that identified significant performance shifts, prompting timely interventions and continuous improvement throughout the education system.
    
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education \& Skills}

\begin{itemize}
    
    \item \textbf{Data Science, Ph.D.}, Bowling Green State University, Ohio, USA \hfill \textit{Sep. 2019 -- May 2024}
    
    \item Physics, M.Sc., Focusing on Nonlinear Optics, specifically thermal effects in Green Lasers.
    
    \item \textbf{Skills: Computer Vision, NLP, LLMs, RAG, Python} (TensorFlow, PyTorch, Scikit-learn, Pandas, NumPy, ipywidgets, GeoPandas), R, SQL, C++, FORTRAN, MATLAB, High-Performance Computing (HPC), Apachi, Hadoop.
    
\end{itemize}

\end{document}
%---------------------------------------------------------------------
